---
title: "RDA-SHARC's Open Science Rewards and Incentives Survey"
execute-dir: project
format: 
  html:
    toc: true
    toc-location: right
    smooth-scroll: true
    html-math-method: katex
    code-fold: true
    self-contained: true
editor: source
author: 'Florencia Grattarola'
date: "`r format(Sys.time(), '%Y-%m-%d')`"
---

```{r}
#| label: setup
#| echo: false
#| eval: true
#| message: false

knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, 
                      dpi=300, 
                      tidy.opts=list(width.cutoff=40), tidy=TRUE,
                      options(scipen = 1, digits = 2))
```

```{r}
#| label: library-data
#| echo: false
#| eval: true
#| message: false

library(ltm)
library(knitr)
library(webr)
library(lubridate)
library(janitor)
library(plyr)
library(likert)
library(rnaturalearth)
library(sf)
sf::sf_use_s2(FALSE)
library(tidyverse)

survey <- read_csv('data/data_survey_aggregated.csv')
survey <- survey %>% 
  remove_empty(c('rows', 'cols')) %>% 
  clean_names() 

# simplify gender field
survey <- survey %>% 
  mutate(gender=ifelse(grepl('female|F|여|féminin|Woman|mujer|femenino',
                             your_gender, ignore.case = T), 'female', 
                       ifelse(grepl('Male|male|M|남|masculino', 
                                    your_gender, ignore.case = F), 'male', 
                              ifelse(grepl('binary|queer', 
                                    your_gender, ignore.case = F), 'non-binary / gender-queer',
                              'no response'))))

# disciplines
disciplines <- survey %>% 
  rename(disciplines=starts_with('what_are_your_main_disciplinary_fields')) %>% 
  select(disciplines) 

world <- ne_countries(scale = 50, returnclass = 'sf') %>% 
  select(name)

world_survey <- left_join(world,
  survey %>% 
    group_by(which_country_do_you_work_in) %>% count() %>% 
    rename(name=which_country_do_you_work_in, responses=n) %>% 
    mutate(name=ifelse(name=='Korea, Rep.', 'South Korea',
                          ifelse(name=='United States', 'United States of America', name)))) %>% 
  select(name, responses) 
```

This survey addresses awareness of Open Science activities and existing & expected reward systems in research assessment, in particular for sharing activities, in different contexts.    

**Quick summary** of respondents background: We received `r nrow(survey)` responses, from people working in `r length(unique(survey$which_country_do_you_work_in))` countries, of which `r nrow(filter(survey, gender=='female'))/nrow(survey)*100`% declare their gender was female, `r nrow(filter(survey, gender=='male'))/nrow(survey)*100`% male, `r nrow(filter(survey, gender=='non-binary / gender-queer'))/nrow(survey)*100`% non-binary or gender-queer and `r nrow(filter(survey, gender=='no response'))/nrow(survey)*100`% had no response. Most respondents had 'Researcher' as their main job title (`r nrow(filter(survey, main_position_job_title_which_of_the_following_are_you_now=='Researcher'))/nrow(survey)*100`%), were affiliated to a 'University' (`r nrow(filter(survey, please_select_the_type_of_organisation_you_are_primarily_affiliated_with=='University'))/nrow(survey)*100`%) or a 'Research institute' (`r nrow(filter(survey, please_select_the_type_of_organisation_you_are_primarily_affiliated_with=='Research institute'))/nrow(survey)*100`%), and had between 10 and 20 years of experience in their field (`r nrow(filter(survey, how_long_have_you_been_working_in_your_field=='10-20 years'))/nrow(survey)*100`%).  


We calculated **Cronbach's alpha** to assess the reliability of the questions that used binary, Likert, and ordinal scales, revealing an acceptable internal consistency.

```{r}
#| label: cronbachs-alpha
#| echo: true
#| eval: true

survey %>% 
  select(starts_with('are_you_familiar_with'),
         starts_with('are_you_involved_in_some_of_the_following'),
         starts_with('does_your_institute_organisation'),
         starts_with('could_you_please_specify_to_what_extent'),
         how_long_have_you_been_working_in_your_field) %>%
  mutate(across(starts_with('are_you')|starts_with('does_your'), 
                ~ case_when(.=='Yes' ~ 1,
                            .=='No' ~ 0,
                            .default = NA))) %>% 
  mutate(across(starts_with('could_you'), 
                ~ case_when(.=='Definitely Not' ~ -2,
                            .=='Probably Not' ~ -1,
                            .=='Possibly' ~ 0,
                            .=='Very Probably' ~ 1,
                            .=='Definitely' ~ 2,
                            .default = NA))) %>% 
  mutate(across(starts_with('how_long'),
               ~ case_when(.=='< 5 years' ~ 1,
                          .=='5-10 years' ~ 2,
                          .=='10-20 years' ~ 3,
                          .=='> 20 years' ~ 4,
                          .default = NA))) %>% 
  cronbach.alpha(CI=T, na.rm = T)

```
# Section 1

## Are you familiar with Open Science?

```{r}
#| label: familiar-with-OS
#| echo: true
#| eval: true
#| message: false

survey %>% 
    group_by(are_you_familiar_with_open_science) %>% 
    count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(n / sum(n))) %>%
  rename(`Are you familiar with Open Science?`= 
           are_you_familiar_with_open_science)  %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

# general
survey %>% 
    group_by(are_you_familiar_with_open_science) %>% 
    count() %>% 
    ggplot(aes(y=n, x='', fill=are_you_familiar_with_open_science)) +
    geom_bar(stat = "identity", position = 'fill') +
    scale_y_continuous(labels = scales::percent_format()) +
    scale_fill_brewer(palette = "Set1") +
    theme_light() + 
    labs(fill='Are you familiar\nwith Open Science?', x='', y='')
```

## Are you involved in some of the following Open Science activities?

```{r }
#| label: involve-in-OS-activities
#| echo: true
#| eval: true
#| message: false

# Select only the likert items in the survey
items_involved <- select(survey, starts_with("are_you_involved_in_some_of"))

# Rename the items so that the question statement becomes the name
names(items_involved) <- c("Sharing a research manuscript as a preprint",
  "Publishing a paper or monograph book as open access",
  "Preregistration of the study design, methods, hypothesis etc., prior to commencing the research",
  "Open or FAIR data management and sharing (for research data, software, models, algorithms, workflows etc.)",
  "Participation in open peer review (being reviewed or the reviewer)",
  "Participation in public engagement, including citizen or community science",
  "Collaboration via virtual research environments or virtual laboratories",
  "None of the above")

# We don't want this option
items_involved <- items_involved %>% select(-`None of the above`)

# A custom function to recode numerical responses into ordered factors
likert_recode_yn <- function(x) {
  y <- factor(x, levels = c("No", "Yes"), exclude="N/A")
  return(y)
}

# Transform the items into factors and save the data set as a likert object
items_involved <- items_involved %>%
  mutate_all(likert_recode_yn) %>% as.data.frame() %>% 
  likert::likert()

# percentages
items_involved$results %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position")) %>% 
  kableExtra::column_spec(1, width = "30em")

# plot
likert.bar.plot(items_involved,
                plot.percent.low = FALSE,
                plot.percent.high = FALSE,
                col=c("#D7B365","#59B4AB"),
                wrap=40,
                plot.percents = TRUE) +
    ggpubr::theme_cleveland() +
    theme(legend.position="bottom")

```

## Are you familiar with the FAIR (Findable, Accessible, Interoperable, and Reusable) principles?

```{r}
#| label: familiar-with-FAIR
#| echo: true
#| eval: true
#| message: false

survey %>% 
  group_by(are_you_familiar_with_the_fair_findable_accessible_interoperable_and_reusable_principles_defined_here) %>% 
  count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(n / sum(n))) %>% 
  rename(Responses=
           are_you_familiar_with_the_fair_findable_accessible_interoperable_and_reusable_principles_defined_here) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

# general
survey %>% 
    group_by(are_you_familiar_with_the_fair_findable_accessible_interoperable_and_reusable_principles_defined_here) %>% 
    count() %>% 
    ggplot(aes(y=n, x='', 
               fill=are_you_familiar_with_the_fair_findable_accessible_interoperable_and_reusable_principles_defined_here)) +
    geom_bar(stat = "identity", position = 'fill') +
    scale_y_continuous(labels = scales::percent_format()) +
    scale_fill_brewer(palette = "Set1") +
    theme_light() + 
    labs(fill='Are you familiar\nwith the FAIR principles?', x='', y='')
```

## Are you involved in some steps of data FAIRification process?

```{r}
#| label: involved-in-FAIRification
#| echo: true
#| eval: true
#| message: false

survey %>% 
  group_by(are_you_involved_in_some_steps_of_data_fai_rification_process_such_as_those_referred_to_here) %>% 
  count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(n / sum(n))) %>% 
  rename(Responses=
           are_you_involved_in_some_steps_of_data_fai_rification_process_such_as_those_referred_to_here) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

# general
survey %>%
  rename(response=are_you_involved_in_some_steps_of_data_fai_rification_process_such_as_those_referred_to_here) %>% 
  group_by(response) %>% 
  count() %>% 
  ggplot(aes(x='', y=n, fill=fct_relevel(response, "No", "Yes", "N/A"))) +
  geom_bar(stat = "identity", position = 'fill') +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette = "Set1") +
  theme_light() + 
  labs(fill='Are you involved in\nsome steps of data\nFAIRification process?', x='', y='')
```

## Does your institute/organisation have policies on various Open Science activities?

```{r}
#| label: organisation-OS-policies
#| echo: true
#| eval: true
#| message: false

survey %>% 
  group_by(does_your_institute_organisation_have_policies_on_various_open_science_activities) %>% 
  count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(n / sum(n))) %>% 
  rename(Responses=
           does_your_institute_organisation_have_policies_on_various_open_science_activities) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

# general
survey %>% 
  rename(response=does_your_institute_organisation_have_policies_on_various_open_science_activities) %>% 
  group_by(response) %>% 
  count() %>% 
  ggplot(aes(x='', y=n, fill=fct_relevel(response, "No", "Yes", "N/A"))) +
  geom_bar(stat = "identity", position = 'fill') +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette = "Set1") +
  theme_light() +
  labs(fill='Does your institute/\norganisation have policies\non various Open Science\nactivities?', x='', y='')
```

# Section 2

## Could you please specify to what extent you feel the following activities should be credited / rewarded? 

Rewards may include career promotion, grants/funding/prizes, gained credits in a research evaluation procedure, authorship/ contributorship, increased academic visibility.

```{r}
#| label: likert
#| echo: true
#| eval: true
#| fig.width: 14
#| fig.height: 6

# Select only the likert items in the survey
items <- select(survey, 
                starts_with(c("could_you_please_specify_to_what_extent")))

# Rename the items so that the question statement becomes the name
names(items) <- c(
  "Sharing a research manuscript as a preprint",
  "Publishing a paper or monograph book as open access",
  "Preregistration of the study design, methods, hypothesis etc., prior to commencing the research",
  "Open or FAIR data management and sharing (for research data, software, models, algorithms, workflows etc.)",
  "Participation in open peer review (being reviewed or the reviewer)",
  "Participation in public engagement, including citizen or community science",
  "Collaboration via virtual research environments or virtual laboratories")

# A custom function to recode numerical responses into ordered factors
likert_recode <- function(x) {
  y <- factor(x, 
              levels = c("Definitely Not","Probably Not", 
                         "Possibly", "Very Probably", "Definitely"), 
                          exclude="No opinion")
  return(y)
}

# Transform the items into factors and save the data set as a likert object
items_likert <- items %>%
  mutate_all(likert_recode) %>% as.data.frame() %>% 
  likert::likert()

# percentages
items_likert$results %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position")) %>% 
  kableExtra::column_spec(1, width = "10em")

# plot
likert.bar.plot(items_likert,
                wrap=30,
                centered = F,
                plot.percent.neutral = TRUE,
                plot.percent.low = TRUE, 
                plot.percent.high = TRUE) + 
    ggpubr::theme_cleveland() +
    theme(legend.position="bottom")  

```

# Section 3

## Does your institute/organisation have any initiative or tool which gives credits/rewards for Open Science activities?

```{r}
#| label: your-institute-rewards
#| echo: true
#| eval: true

survey %>% 
  group_by(does_your_institute_organisation_have_any_initiative_or_tool_which_gives_credits_rewards_for_open_science_activities) %>% 
  count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(n / sum(n))) %>% 
  rename(Responses=
           does_your_institute_organisation_have_any_initiative_or_tool_which_gives_credits_rewards_for_open_science_activities) %>% 
  knitr::kable(digits = 2) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

# general
survey %>%
  rename(response=does_your_institute_organisation_have_any_initiative_or_tool_which_gives_credits_rewards_for_open_science_activities) %>% 
  group_by(response) %>% 
  count() %>% 
  ggplot(aes(y=n, x='', fill=response)) +
  geom_bar(stat = "identity", position = 'fill') +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette = "Set1") +
  theme_light() + 
  labs(fill='Does your institute/organisation\nhave any initiative or tool which\ngives credits/rewards for\nOpen Science activities?', x='', y='')

# by country
survey %>%
  rename(response=does_your_institute_organisation_have_any_initiative_or_tool_which_gives_credits_rewards_for_open_science_activities,
         country=which_country_do_you_work_in) %>% 
  group_by(response, country) %>% 
  count() %>% filter(response=='Yes') %>% ggplot(aes(y=n, x=country, fill=country)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Spectral") +
  scale_fill_manual(values = colorRampPalette(RColorBrewer::brewer.pal(9, "Set1"))(15)) +
  theme_light() + theme(axis.text.x = element_text(size=rel(0.5))) +
  labs(caption ='Mentioned initiative or tool which gives credits/rewards for Open Science activities by country', fill='', x='', y='')

```

# Section 4

## How would you want the previously mentioned Open Science activities to be rewarded?

### Labels 

```{r}
#| label: how-would-you-like-to-OS-be-rewarded-word-cloud
#| echo: true
#| eval: true
#| out.width: 100%
#| fig-height: 8
#| fig-dpi: 200

rewardLabels <- survey %>%
  rename(labels=suggested_rewards_categorised_according_to_shar_cs_rewarding_terminology) %>% 
    separate_rows(labels, sep = ';') %>% 
    mutate(labels=str_squish(labels)) %>%
    filter(!is.na(labels) & labels!='') %>% 
    mutate(labels=ifelse(labels=="good science\'", "\'good science\'", labels)) %>% 
    mutate(labels=ifelse(labels=='funding/grants for OS activitie',
                       'funding/grants for OS activities', labels)) %>% 
    mutate(labels=ifelse(labels=='OS indicators in research evaluation processes',
                       'OS indicators in research evaluation and/or career progression processes', labels))

rewardLabels %>% 
  group_by(labels) %>% 
  count() %>% arrange(desc(n)) %>% ungroup() %>% 
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(`SHARC Rewards Terminology`=labels) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

rewardLabels %>% filter(!is.na(labels)) %>%
  group_by(labels) %>% count() %>% 
  ggplot(aes(x='', y=n, fill=fct_reorder(labels, n))) +
  geom_bar(stat = "identity", position = 'fill') +
  guides(fill=guide_legend(ncol=1)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = colorRampPalette(RColorBrewer::brewer.pal(9, "Set1"))(19)) +
  theme_light() + 
  labs(fill='SHARC Rewards\nTerminology', x='', y='') +
  theme(legend.position="right")

most_common_rewards <- c(
  'OS indicators in research evaluation and/or career progression processes',
  'funding/grants for OS activities',
  'awards/bonuses',
  'research visibility indicators',
  'authorship/contributorship'
)

rewardLabels %>% filter(!is.na(labels)) %>%
  mutate(labels=ifelse(!labels %in% most_common_rewards,
                           'others', labels)) %>% 
  group_by(labels) %>% count() %>% 
  ggplot(aes(x='', y=n, fill=fct_relevel(fct_reorder(labels, n), 'others'))) +
  geom_bar(stat = "identity", position = 'fill') +
  guides(fill=guide_legend(ncol=1)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette="Set1") +
  ggpubr::theme_cleveland() + 
  labs(fill='SHARC Rewards\nTerminology', x='', y='') +
  theme(legend.position="right")

```

# Respondents' background

## Gender

These are the different responses and how they were classified. I now added 'non-binary' as a different category and tagged all other as 'other responses'.

```{r}
#| label: gender-responses
#| echo: true
#| eval: true
#| message: false
#| tbl-cap: Gender responses
survey %>% distinct(your_gender, gender) %>% kable()
```

  -   Your gender

```{r}
#| label: gender
#| echo: true
#| eval: true
#| message: false

survey %>% 
  group_by(gender) %>% 
  count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(`Declared gender`= gender) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

survey %>% 
  group_by(gender) %>% 
  count() %>% 
  ggplot(aes(x='', y=n, fill=gender)) + 
  geom_bar(stat = "identity", position = 'fill' ) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette = "Dark2") +
  theme_light() + 
  labs(fill='Gender', x='', y='')


survey %>% 
  rename(response=which_country_do_you_work_in) %>%
  mutate(response_x=ifelse(response!='Korea, Rep.'&response!='France'&
                             response!='United States'&response!='Uruguay',
                           'Other countries', response)) %>% 
  group_by(response_x) %>%
  count()  %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(Country= response_x) %>% arrange(desc(n)) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

```

## Country

  - Which country do you work in?
  
```{r}
#| label: country
#| echo: true
#| eval: true
#| message: false

survey %>% 
  group_by(which_country_do_you_work_in) %>% 
  count() %>%  ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(Country= which_country_do_you_work_in) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

# which_country_do_you_work_in
survey %>% 
    rename(response=which_country_do_you_work_in) %>%
    group_by(response) %>%
    count() %>%  
    ggplot(aes(x='', y=n, fill=fct_reorder(response, desc(n)))) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = colorRampPalette(RColorBrewer::brewer.pal(9, "Set1"))(37)) +
    theme_light() + 
    labs(caption = 'Which country do you work in?', fill='', x='', y='')

# Korea, France, USA, Uruguay, and Other countries
survey %>% 
  rename(response=which_country_do_you_work_in) %>%
  mutate(response_x=ifelse(response!='Korea, Rep.'&response!='France'&
                            response!='United States'&response!='Uruguay', 
                         'Other countries', response)) %>% 
  group_by(response_x) %>%
  count() %>% 
  ggplot(aes(x='', y=n, fill=fct_relevel(fct_reorder(response_x, n), 'Other countries')), show.legend = FALSE) +
  geom_bar(stat = "identity", position = 'fill') +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette = "Spectral") + labs(fill='') + 
  theme_light() + 
  labs(caption ='Which country do you work in?', x='', y='')

survey %>% 
  rename(response=which_country_do_you_work_in) %>%
  mutate(response_x=ifelse(response!='Korea, Rep.'&response!='France'&
                             response!='United States'&response!='Uruguay',
                           'Other countries', response)) %>% 
  group_by(response_x) %>%
  count() %>%  ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(Country= response_x) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))
```

### Map 

```{r}
#| label: map
#| echo: true
#| eval: true
#| message: false

# map plot
world_survey %>%
    st_cast('POLYGON') %>% 
    mutate(responses=ifelse(name=='France' & grepl('-52', geometry), NA, responses)) %>% 
    mutate(name=ifelse(name=='France' & is.na(responses), 'French Guyana', name)) %>% 
    group_by(name) %>% 
    dplyr::summarise(responses=max(responses)) %>%  ggplot() + geom_sf(aes(fill=responses), size=0.1) +
    scale_fill_fermenter(palette ='Spectral', 
                         breaks=c(0,1,2,3,4,5,10,15,20,25,39),
                         na.value = 'grey95') +
    theme_minimal() +
    labs(fill='N') 
```

## Job title

  -   Main position/job title: which of the following are you now?

```{r}
#| label: job-title
#| echo: true
#| eval: true
#| message: false

survey %>% 
  rename(response=main_position_job_title_which_of_the_following_are_you_now) %>%
  group_by(response) %>% 
  count() %>% arrange(desc(n)) %>%ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(`Job title`= response) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))
```

## Experience in the field

  -   How long have you been working in your field?

```{r}
#| label: years-of-experience
#| echo: true
#| eval: true
#| message: false

survey %>% 
  group_by(how_long_have_you_been_working_in_your_field) %>% 
  count() %>% ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(`Experience in the field`= how_long_have_you_been_working_in_your_field) %>% 
  mutate(index=ifelse(`Experience in the field`=='> 20 years', 1, 
                      ifelse(`Experience in the field`=='10-20 years', 2, 
                             ifelse(`Experience in the field`=='5-10 years', 3, 
                                    ifelse(`Experience in the field`=='< 5 years', 4, 5))))) %>% 
  arrange(index) %>% select(-index) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

survey %>% 
    rename(response=how_long_have_you_been_working_in_your_field) %>% 
    group_by(response) %>%
    count() %>%
    filter(!is.na(response)) %>% 
    ggplot(aes(x='', y=n, fill=fct_relevel(response,
                                           '> 20 years',
                                           '10-20 years',
                                           '5-10 years',
                                           '< 5 years'))) +
    geom_bar(stat = "identity", position = 'fill' ) +
    scale_y_continuous(labels = scales::percent_format()) +
    scale_fill_brewer(palette = "Spectral") +
    theme_light() + 
    labs(fill='Years of experience', x='', y='')

```

## Affiliation type of organisation

  -   Please select the type of organisation you are primarily affiliated with

```{r}
#| label: type-of-organisation
#| echo: true
#| eval: true
#| message: false

survey %>% 
  rename(response=please_select_the_type_of_organisation_you_are_primarily_affiliated_with) %>%
  group_by(response) %>% 
  count() %>% arrange(desc(n))%>% ungroup() %>%
  mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
  rename(`Type of organisation`= response) %>% 
  kableExtra::kbl(booktabs = T) %>% 
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"))
```

## Disciplinary fields

  -   What are your main disciplinary fields (up to 3; e.g., computer science, physics, biology, medicine)?
  
This plot is generated by classifying the disciplines according to **Wikipedia**'s [Outline of academic disciplines](https://en.wikipedia.org/wiki/Outline_of_academic_disciplines).


```{r}
#| label: disciplinary-fields
#| echo: true
#| eval: true
#| message: false
#| out-width: 90%
#| fig-dpi: 200
#| tbl-cap: 'List of disciplines'

# disciplines
disciplines <- survey %>% 
  rename(disciplines=starts_with('what_are_your_main_disciplinary_fields')) %>% 
  select(response_id, disciplines) %>% 
  separate_rows(disciplines, sep = ';') %>% 
  mutate(disciplines=str_squish(disciplines) %>% str_to_lower())

new_wiki_disciplines <- read_csv('data/disciplines.csv')
disciplines_for_plot <- left_join(disciplines, new_wiki_disciplines)

disciplines_for_plot %>% 
    filter(!is.na(subfield)) %>% 
    group_by(field) %>% count() %>% arrange(desc(n)) %>% ungroup() %>%
    mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
    rename(Field=field) %>% 
    kableExtra::kbl(booktabs = T) %>% 
    kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

disciplines_for_plot %>% 
    filter(!is.na(subfield)) %>% 
    group_by(field, subfield) %>% count() %>% arrange(field, desc(n)) %>% ungroup() %>% head(n=25) %>% 
    mutate(`%` = scales::label_percent()(round(n / sum(n), 3))) %>% 
    rename(Field=field, `Sub-field`= subfield) %>% 
    kableExtra::kbl(booktabs = T) %>% 
    kableExtra::kable_styling(latex_options = c("striped", "hold_position"))

disciplines_for_plot %>% 
  filter(!is.na(subfield)) %>% 
  group_by(field, subfield) %>% count() %>% 
  PieDonut(aes(field, subfield, count=n), 
           showPieName = F,
           showRatioThreshold = 0.02,
           labelposition = 1,
           ratioByGroup = F)

```
